\Large{Adversarial Variational Optimization of Non-Differentiable Simulators}

### 2017-06-20 paper.tex
add algo

    \begin{flushleft}
        {\it Inputs:} observed data $\{ \mathbf{x}_i \}_{i=1}^N$, simulator $g$;\\
        {\it Outputs:} proposal distribution $q_\psi(\theta)$;\\
        {\it Hyper-parameters:} Number $T$ of training iterations,
                                Number $K$ of gradient steps to update $d$,
                                Size $M$ of the minibatches.
    \end{flushleft}

    \label{alg:avo}
    \begin{algorithmic}[1]
        \State{\glnote{todo!}}
        \For{$t=1$ to $T$}
            % \For{$k=1$ to $K$} \Comment{Update $r$}
            %     \State{Sample minibatch $\{x_m, z_m, s_m = f(x_m;\theta_f) \}_{m=1}^M$} of size $M$;
            %     \State{With $\theta_f$ fixed, update $r$ by ascending its stochastic gradient $\nabla_{\theta_r} E(\theta_f, \theta_r) :=$
            %     $$\nabla_{\theta_r} \sum_{m=1}^M \log p_{\theta_r}(z_m|s_m)  ;$$}
            % \EndFor
            % \State{Sample minibatch $\{x_m, y_m, z_m, s_m = f(x_m;\theta_f)  \}_{m=1}^M$} of size $M$; \Comment{Update $f$}
            % \State{With $\theta_r$ fixed, update $f$ by descending its stochastic gradient $\nabla_{\theta_f} E(\theta_f, \theta_r) :=$
            % $$\nabla_{\theta_f}  \sum_{m=1}^M \left[ -\log p_{\theta_f}(y_m|x_m)  +\log p_{\theta_r}(z_m|s_m)  \right],$$
            % \indent where $p_{\theta_f}(y_m|x_m)$ denotes $\mathbf{1}(y_m=0)(1-s_m) + \mathbf{1}(y_m=1)s_m$;}
        \EndFor
    \end{algorithmic}
    \end{algorithm}
    \end{minipage}
\end{figure*}

@@

Practically, the variational objectives \ref{eqn:vo-ud}-\ref{eqn:vo-ug}
have the effect of replacing the modeled data distribution of Eqn.~\ref{eqn:p_theta} with
a distribution parameterized in terms of $\psi$:
\begin{equation}\label{eqn:p_psi}
    \mathbf{x} \sim p_\psi \equiv \mathbf{z} \sim p_z, \theta \sim q_\psi, \mathbf{x} = g(\mathbf{z}; \theta).
\end{equation}
Intuitively, this corresponds to a family of simulators, each configured
with randomly sampled parameters $\theta \sim q_\psi$, whose joint collection
of generated samples is optimized with adversarial training to approach the real data distribution $p_r$.
However, this formulation does not necessarily guarantee that the
proposal distribution $q_\psi$ will place its mass arbitrarily tight
around the parameters of interest $\theta^*$. For this purpose, we augment Eqn.~\ref{eqn:vo-ug}
with a regularization term corresponding to the differential entropy $H$ of
the proposal distribution. That is,
\begin{equation}
    U_g = \mathbb{E}_{\theta \sim q_\psi} [ {\cal L}_g ] + \lambda H(q_\psi)
\end{equation}
where $\lambda \in \mathbb{R}^+$ is a hyperparameter controlling the trade-off
between the generator objective and the tightness of the proposal distribution.
For large values of $\lambda$, the procedure is constrained to fit a proposal
distribution with low entropy, which has the effect of concentrating its density
tightly around one or a few $\theta$ values. On the other hand, for small values of $\lambda$,
proposal distributions with larger entropy are not penalized, which may result
in learning a smeared variation of the original simulator.

>>>>

    \begin{flushleft}
        {\it Inputs:} observed data $\{ \mathbf{x}_i \}_{i=1}^N$, simulator $g$;\\
        {\it Outputs:} proposal distribution $q_\psi(\theta)$;\\
        {\it Hyper-parameters:} The number $n_{\text{critic}}$ of training iterations of $d$; the gradient penalty coefficient $\lambda$; the entropy penalty coefficient $\gamma$. 
    \end{flushleft}

    \label{alg:avo}
    \begin{algorithmic}[1]
        \While{$\psi$ has not converged}
            \For{$i=1$ to $n_{\text{critic}}$} \Comment{Update $d$}
                \State{Sample a mini-batch $\{\mathbf{x}_m \}_{m=1}^M \sim p_r$, $\{\mathbf{z}_m \}_{m=1}^M \sim p_z$, $\{\theta_m \}_{m=1}^M \sim q_\psi$, $\{\epsilon_m \}_{m=1}^M \sim U[0,1]$.}
                \For{$m=1$ to $M$}
                    \State{$\tilde{\mathbf{x}}_m \leftarrow g(\mathbf{z}_m; \theta_m)$}
                    \State{$\hat{\mathbf{x}}_m \leftarrow \epsilon_m \mathbf{x}_m + (1 - \epsilon_m) \tilde{\mathbf{x}}_m$}
                    \State{$L^{(m)} \leftarrow d(\tilde{\mathbf{x}}_m; \phi) - d(\mathbf{x}_m; \phi) + \lambda (|| \nabla_{\hat{\mathbf{x}}_m} d(\hat{\mathbf{x}}_m; \phi) ||_2 - 1)^2 $}
                \EndFor
                \State{$\phi \leftarrow \text{RMSProp}(\nabla_\phi \tfrac{1}{M} \sum_{m=1}^M L^{(m)})$}
            \EndFor
            \State{Sample a mini-batch $\{\mathbf{z}_m \}_{m=1}^M \sim p_z$, $\{\theta_m \}_{m=1}^M \sim q_\psi$.}  \Comment{Update $q_\psi$}
            \State{$\psi \leftarrow \text{RMSProp}(\tfrac{1}{M} \sum_{m=1}^M -d(g(\mathbf{z}_m; \theta_m)) \nabla_\psi \log q_\psi(\theta_m) + \nabla_\psi \gamma q_\psi(\theta_m) \log q_\psi(\theta_m))$}
        \EndWhile
    \end{algorithmic}
    \end{algorithm}
    \end{minipage}
\end{figure*}

@@

Practically, the variational objectives \ref{eqn:vo-ud}-\ref{eqn:vo-ug}
have the effect of replacing the modeled data distribution of Eqn.~\ref{eqn:p_theta} with
a distribution parameterized in terms of $\psi$:
\begin{equation}\label{eqn:p_psi}
    \mathbf{x} \sim p_\psi \equiv \mathbf{z} \sim p_z, \theta \sim q_\psi, \mathbf{x} = g(\mathbf{z}; \theta).
\end{equation}
Intuitively, this corresponds to a family of simulators, each configured
with randomly sampled parameters $\theta \sim q_\psi$, whose joint collection
of generated samples is optimized with adversarial training to approach the real data distribution $p_r$.
However, this formulation does not necessarily guarantee that the
proposal distribution $q_\psi$ will place its mass arbitrarily tight
around the parameters of interest $\theta^*$. For this purpose, we augment Eqn.~\ref{eqn:vo-ug}
with a regularization term corresponding to the differential entropy $H$ of
the proposal distribution. That is,
\begin{equation}
    U_g = \mathbb{E}_{\theta \sim q_\psi} [ {\cal L}_g ] + \gamma H(q_\psi)
\end{equation}
where $\gamma \in \mathbb{R}^+$ is a hyperparameter controlling the trade-off
between the generator objective and the tightness of the proposal distribution.
For large values of $\gamma$, the procedure is constrained to fit a proposal
distribution with low entropy, which has the effect of concentrating its density
tightly around one or a few $\theta$ values. On the other hand, for small values of $\gamma$,
proposal distributions with larger entropy are not penalized, which may result
in learning a smeared variation of the original simulator.
